\documentclass[12pt,a4paper]{article} % Could set draft on here for more speed but no images
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{todo}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\author{Eric van der Toorn}
\title{Summaries}
\begin{document}
\maketitle
\section{Introduction}
I'll start with an introduction of my general ambition with this document, which is quite simply to record a personal summary and reflection for each of the books I've read or listened to. I have some catching up to do, and I'll start with outlining A. Why I'm doing this, and B. Which books I still have to do this for. Then I'll start with at least 2 of the books within this same paper before creating a structure, because I know from myself that I can get quite distracted/ dwell away from the main point if I do that first.
\subsection{Reasons}
This has been a thought in the back of my mind for a while, and it actually came up quite recently when I was having a discussion with Timotheos, a guest lecturer for the Growth: Managing Your Firm course. We were talking about some of the books we had read and I mentioned how it could get quite mixed up. Then he started talking about how he had a document which collected the books he had read (or at least a subset of them) with summaries and reflections. I agreed that it would be quite a useful thing, and he expounded with another reason: even if you stop with it, a few years later you may reread one of the books and close it with a different viewpoint, which you can then further reflect on. He also mentioned that the document he uses is not intended for modification, only being open for extension.
In general, I can tell for myself that the books I've read that I find useful get clearer in my memory when I focus on my specific memories of reading them, and that I actually feel excited for doing this kind of summary, so hopefully we'll have some fun doing this. I find that the more I write the more I am excited to write more, so let's continue!

\section{List of books}
It is hard to decide which books to do first, but I actually think I will treat it as a stack $->$ Last In First Out, as that way I can discuss the things that are most recent to me and best in my memory first. 
First a list of books that I am currently reading or want to read because they keep popping up in my head:
\subsection{Reading list}
\begin{itemize}
\item 12 Rules for Life (Jordan B. Peterson) - Quite the interesting guy talking about rules you can and should apply to your life
\item Predictable Irrational (Dr. Dan Aley) - Outlining some very interesting things in which humans are ever so irrational.

\item The Great Ideas of Psychology (Daniel N. Robinsson) [ON HOLD] - A summary of psychology from its very roots to its current state.
\end{itemize}
\subsection{Wish list}
\begin{itemize}

\item Black Swan, the impact of the highly improbable (...) [UNSTARTED] - ...
\item Zero to One - Dad really recommends this one
\item 50 lessons I learned from the world (Vic Johnson) - Interesting title and dad finished it
\item De meeste mensen deugen - Dad basically really admires the book
\item Homo Deus - All the other books of Harari have been great
\item Awaken the Giant within | Giant Steps (Tony Robbins) - Want to read and do this one during a vactation or when I have a span of free time large enough.
\item Nudge - Seems like a good book, was quite recommended
\item Find out anything from anyone ...

\end{itemize}
\subsubsection{Considering}
A list of books I'm considering, starting with the books recommended by Nadav (from Growth - Managing Your Firm)
\begin{itemize}
\item At the mind’s limits (Jean Amery)
\item Man’s search for meaning (Viktor Frankl)
\item Fear of freedom (Erich Fromm)
\item In the realm of hungry ghosts (Gabor Mate)
\item The abolition of man (CS Lewis)
\item I and Thou (Martin Buber)
\item Sovereignty of goodness (Iris Murdoch)
\item The malaise of modernity (Charles Taylor)
\item Intimate history of humanity (Theodor Zeldin)
\end{itemize}

\subsection{Read books}

\begin{itemize}
\item Mindset: The new Psychology of success. By Carol S. Dweck, a book expounding the Fixed and Growth mindsets.

\item Crucial Conversations, tools for talking when the stakes are high (Kerry Patterson, Joseph Grenny, Ron McMillan, and Al Switzler), a review on how the authors discovered that one of the major factors that makes people succeed in getting things done, both in business and elsewhere, was the ability to have crucial conversations.
\item Cognitive Behavioral Therapy (Dr. Sattersfield) -  A course on CBT, but still good enough that I feel like it requires a summary in order to remind myself of its major points
\item The 7 Habits of HIghly Effective People (Stephen R. Covey) - A book in which the author names and explains seven habits that are useful to apply, resulting in becoming more effective as a person. Interesting side note: first three are about the self, last four about interacting with others. You have to mold yourself before increasing your effectiveness(?) with others.
\item How to Talk to Anyone (Leil Lowndes) - 92 tips and tricks to interacting with others, some of which can actually be quite useful and fun to apply ;) Side note: will probably list all the tips shortly
\item The Wellbeing Quotient - Elements that contribute to my wellbeing
\item Leadership in a Complex World - A course I followed at the TU Delft as part of the honours programme; really fun and engaging, so I want to document what I learned here.
\item What the most successful people fo before breakfast (Laura Vanderkam) - Taught me the importance of a good morning ritual
\item No excuses  (Brian Tracy) - Quite a simple book on how you shouldn't blame things, just take responsibility or let it go (?)
\item The go-giver - how giving can be way more helpful than just taking - When done the right way
\item 21 lessons of the 21st Century (Harari) - About the general state of the present and the problems we're facing.
\item Homo Sapiens (Harari) - The past of humanity, beautifully given a new perspective
\item The Longevity Code (Kris Verburgh) - Basically my first non-fiction good book that I read for my pleasure and changed my life
\item Atomic Habits (James Clear) - This is slowly but surely changing my life for the better, learning how to approach changing habits.
\item The Subtle Art of not giving a fuck (Mark Manson) - Choose what you care about, don't let your environment choose for you.
\item Becoming (Michelle Obama) - First autobiography I've read afaik, and it was a great experience, think I'm a fan of hers now.
\end{itemize}

\subsection{Books that are complete and summarized}
Awfully empty to start with
\begin{itemize}
\item \ref{mindsets} Mindsets (Carol S. Dweck)
\item Talking To Strangers, (Malcolm Gladwell), a discussion on why we are so bad at perceiving people we don't know much about.
\item Thinking, Fast and Slow (Daniel Kahlemann) - Separates the mind into two parts, a fast intuitive mind and a slow rational one, and shows some very interesting aspects on the difference.
\end{itemize}


\section{Summaries}

\input{summaries/mindsets-dweck.tex}

\input{summaries/talking-to-strangers-gladwell.tex}

\input{summaries/thinking-fast-and-slow-kahnemann.tex}

\end{document}