\documentclass[a4paper]{article}

%%%%%%%% CREATE DOCUMENT STRUCTURE %%%%%%%%
%% Language and font encoding
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
%\usepackage{subfig}

% \usepackage{titlesec}
% \newcommand{\sectionbreak}{\clearpage}
%% Sets page size and margins
\usepackage[a4paper,top=4cm,bottom=4cm,left=2.5cm,right=2.5cm,marginparwidth=1.75cm]{geometry}
%% Useful packages
\usepackage{amsmath}
\usepackage{array}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=darkblue]{hyperref}
\setlength {\marginparwidth }{2cm}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{caption}
\usepackage{csquotes}
\usepackage{subcaption}
\usepackage{sectsty}
\usepackage{apacite}
\usepackage{float}
\usepackage{titling}
\usepackage{blindtext}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{caption}
\addtolength{\skip\footins}{1pc plus 4pt}
\usepackage{multirow}
%\usepackage{dblfnote}  % Two footnotes in one line

\usepackage{amsthm,amssymb}

\renewcommand{\qedsymbol}{\rule{0.7em}{0.7em}}

\usepackage{xcolor}
\definecolor{darkblue}{rgb}{0.0, 0.0, 0.33} % Used for hyperref package

% Set up ToDo notes package
\newcommand{\todoall}[1]{\todo[inline, caption={}, color=red!40]{Everyone: #1}}
\newcommand{\todoany}[1]{\todo[inline, caption={}, color=orange!40]{Anyone: #1}}

%%%%%%%% DOCUMENT %%%%%%%%
\begin{document}

%%%% Title Page
\begin{titlepage}

\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\center
% University
\textsc{\LARGE Self-Reviews}\\[1cm]

% Document info
\textsc{\Large Personal Development}\\[0.2cm]

\large

\emph{Authors}\\[2mm]

\begin{tabular}{l }
Eric A. van der Toorn
\end{tabular}\\[0.5cm]

\end{titlepage}

\tableofcontents
\newpage
\section{Introduction}

\newpage
\section{2020}

\subsection{Winter Review}
I don't know if I'm remembering this correctly, I think last review was in a notebook which I'm not sure of its location.
Currently I think this list resembles my start of year more than it does the halfway point.
\subsubsection{Before}
\begin{itemize}
 \item Lose weight: Feel less fat on me
 \item Stop playing Rocket League as much
 \item Graduate
 \item Work out more?
 \item Go to bed on time. On that note, off to bed now.
\end{itemize}

\subsubsection{Current}
I'm going to go over this on a monthly basis for now.
\paragraph{August} After having a very nice vacation with the boys (I didn't drink, good self restraint there),
Finished up my honours project (though it was barely adequate and not even close to being worthy of publishing) and decided on my masters.
I kept up the running.
On the constructive side, was hopeless at getting my sleep time on track, with numbers past 12 running rampant, in fact only the very last day of August did I go to bed before midnight, as 23:50.
Registered for both MSc. in Delft and Amsterdam, though because of the reluctance of the Delft adminstration to help I couldn't get the docs for Amsterdam done in time\dots

\paragraph{September}
Went to the gym more, also better gymming, though still gamed quiute a lot.
Started the 75 day challenge...

\paragraph{October}
\subsection{Review}
RL felt more like sinning in the past few months, and I've been exercising quite a bit. On the other hand, I have been eating too much and not healthy enough (though not bad either, just too much mostly). During December/November I decided to only be gaming after 17.00 and that has worked wonders for both my self-restraint which I'm really happy with and my motivation to do actual studying. My study load has been quite high, though I seem to be keeping ahead for most courses except for statistical math courses. MDA and ML will probably be hardest to pass while actually understanding the content.
But they are really quite interesting (MDA at least, haven't done a lot of ML yet). ASB is really quite fun though frustrating.
On another topic, Oscar has gotten a girlfriend and Jimmy has stayed with his, leaving me the only one of the ones I see most frequently `empty-handed'. I don't really like that :( I don't know, maybe invest some more time into relationships sooner rather than later\dots


\subsubsection{Main Challenges}
\begin{itemize}[label=$\mapsto$]
    \item Choosing Exchange places and applying
    \item Choosing potential thesis location
    \item Choosing thesis (topic/location/professor)
    \item Romance?
    \item Getting a good sleeping schedule
    \item Finishing up all my courses
    \item Starting with some coaching
    \item Truly understanding some statistics
    \item Having fun (While doing these things, I can have fun all along ;)
\end{itemize}

\subsection{(New Year's) Resolutions}
\begin{itemize}
    \item mkl
\end{itemize}

\end{document}